Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2025-01-23 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
x paper

library(needs)
needs(
  tidyverse,     # A collection of packages (e.g., ggplot2, dplyr, tidyr) for data manipulation, visualization, and general workflows.
  lubridate,     # For working with dates and times (e.g., parsing, manipulation, arithmetic).
  viridis,       # Provides colorblind-friendly color palettes for plots and visualizations.
  grid,          # A base R package for low-level grid graphics, useful for customizing complex plots.
  gridExtra,     # Extends grid by allowing multiple grid-based plots to be arranged into a single layout.
  cowplot,       # Simplifies creating publication-quality multi-panel plots, often combined with ggplot2.
  readxl,        # For reading Excel files (.xls, .xlsx) into R without requiring external dependencies.
  ARTofR,        # For applying aligned rank transform (ART) to factorial data for nonparametric analysis.
  moments,       # Provides functions to compute statistical moments (e.g., skewness, kurtosis).
  ltm,           # Used for latent trait models, including item response theory (IRT) analysis.
  sjPlot,        # A package to create publication-ready tables and visualizations for statistical models.
  kableExtra,    # Enhances the `knitr::kable()` function for producing polished and customizable tables in R Markdown.
  xtable,        # Converts R objects to LaTeX/HTML tables, especially useful for integration with Sweave/knitr.
  DescTools,     # A toolbox of descriptive statistics, effect size calculations, and data manipulation utilities.
  formattable,   # Allows creation of "formattable" data frames with customized formatting for reporting.
  psych,         # Provides tools for psychological research, including reliability analysis and descriptive statistics.
  apaTables,     # Simplifies the creation of APA-style tables for inclusion in papers or reports.
  rstatix,       # User-friendly pipe-compatible functions for common statistical tests and effect sizes.
  effsize,       # Computes effect sizes (e.g., Cohen's d) for t-tests and other statistical comparisons.
  knitr,         # Enables dynamic reporting by weaving R code and outputs into documents (e.g., R Markdown).
  papaja,        # Helps produce APA-style manuscripts directly from R Markdown.
  afex,          # Performs ANOVAs, including mixed-designs and generalized linear models, with a focus on user-friendliness.
  emmeans,       # Computes estimated marginal means (or least-squares means) for post-hoc comparisons in models.
  corrplot       # Visualize correlation matrices in a visually appealing way.
)

@@

#### Percentage of fixations on each AOI, relative to the total number of fixations during the entire "Lesson" 
```{r nof_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Step 1: Define AOI categories
aoi_columns <- list(
  "AOI_Students" = c(
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ),
  "AOI_Disruptive_Person" = c("Number_of_fixations.Disruptive_Person"),
  "AOI_Teacher_Material" = c(
    "Number_of_fixations.Board_Screen",
    "Number_of_fixations.Material_Teacher"
  ),
  "AOI_Student_Desk" = c(
    "Number_of_fixations.Nametag_Anna",
    "Number_of_fixations.Nametag_Bianca",
    "Number_of_fixations.Nametag_Carl(a)",
    "Number_of_fixations.Material_Students"
  ),
  "AOI_Classroom_Others" = c("Number_of_fixations.Classroom_Others")
)

@@

# # Step 6: Display the table with APA style
# kable(grouped_aoi_percentages, 
#       col.names = c("AOI", "Expert (%)", "Novice (%)"),
#       caption = "Average Fixation Percentage per AOI by Group (Novice vs. Expert) - Descending Order") %>%
#   kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE) %>%
#   add_header_above(c(" " = 1, "Fixation Percentage" = 2)) %>%
#   row_spec(0, bold = TRUE) %>%
#   column_spec(2:3, width = "3em", border_left = TRUE)

# Step 7: Plot with descending AOI order, y-axis limit set to 100%, and percentage labels inside the bars
percentage_number_fixation <-
  ggplot(grouped_aoi_percentages,
         aes(
           x = reorder(AOI, -Fixation_Percentage),
           y = Fixation_Percentage,
           fill = Group
         )) +
  geom_bar(stat = "identity",
           position = position_dodge(width = 0.8),
           width = 0.7) +
  geom_text(
    aes(label = paste0(Fixation_Percentage, "%")),
    position = position_dodge(width = 0.8),
    vjust = -0.3,
    size = 3
  ) +
  labs(title = "Average Fixation Percentage by AOI and Group (Descending Order)", x = "AOI", y = "Fixation Percentage (%)") +
  scale_fill_brewer(palette = "RdBu") +
  theme_cowplot() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  guides(fill = guide_legend(title = "Group")) +
  ylim(0, 100)  # Set y-axis limit to 100%

ggsave(filename = "plots/percentage_number_fixation.svg",
       width = 20,
       height = 12,
       units = "cm")

@@

# Initialize an empty data frame to store the results
results <- data.frame()

@@

      # Format the results for the current AOI and add to the results data frame
      results <- rbind(
        results,
        data.frame(
          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
          "Group Comparison" = "Experts vs. Novices",
          "t-value" = round(t_test_result$statistic, 2),
          "df" = t_test_result$parameter,
          "p-value" = format.pval(t_test_result$p.value, digits = 2, eps = .05),
          "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
          "Cohen's d" = round(cohen_d_value, 2),
          "95% CI (d)" = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
        )
      )

    } else {
      # If one group has no data, append N/A values for this AOI
      results <- rbind(
        results,
        data.frame(
          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
          "Group Comparison" = "Experts vs. Novices",
          "t-value" = NA,
          "df" = NA,
          "p-value" = NA,
          "Mean Difference" = NA,
          "Cohen's d" = NA,
          "95% CI (d)" = NA
        )
      )
    }
  }
}

# Clean up AOI names for readability in the final table
aoi_name_mapping <- c(
  "AOI_Students" = "Students",
  "AOI_Disruptive_Person" = "Disruptive Person",
  "AOI_Teacher_Material" = "Teacher Material",
  "AOI_Student_Desk" = "Student Desk",
  "AOI_Classroom_Others" = "Classroom/Others"
)
results$AOI <- aoi_name_mapping[results$AOI]

# Display the combined results table in APA style without row names
knitr::kable(results, caption = "t-Test and Effect Size for Fixation Percentage across AOIs (Experts vs. Novices)", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

#### Number of fixations per minute (micro-teaching unit)
```{r nof_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

##################### NUMBER OF FIXATIONS PER MINUTE IN MICRO-TEACHING UNIT ########################

# 1. Data Preparation: Filter and Calculate Fixations per Minute in Micro-Teaching Unit
df_aoi_sum <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Group,
    Participant,
    Duration_of_interval,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    -contains("Disruptive_Person")
  ) %>%
  rowwise() %>%
  transmute(
    Group = Group,
    Participant = Participant,
    Duration_of_interval_min = round(Duration_of_interval / 60000, 2),
    Duration_of_interval_sec = round(Duration_of_interval / 1000, 2),
    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Number_fixation_min_mtu = round(Sum_number_fixation / Duration_of_interval_min, 2),
    Group = as_factor(Group)
  ) %>%
  drop_na()

# 2. Descriptive Statistics Table for Number of Fixations per Minute
nof_table <- df_aoi_sum %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    M = round(mean(Number_fixation_min_mtu), 2),
    SD = round(sd(Number_fixation_min_mtu), 2),
    Min = round(min(Number_fixation_min_mtu), 2),
    Max = round(max(Number_fixation_min_mtu), 2)
  )

# Display the descriptive table in APA style
knitr::kable(nof_table, caption = "N, M, SD, Min & Max Number of Fixations per Minute (Micro-Teaching Unit)") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# 3. Calculate means and standard deviations for Novice and Expert
mean_novice_mtu <- round(mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
sd_novice_mtu <- round(sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Novice"], na.rm = TRUE), 2)
mean_expert_mtu <- round(mean(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)
sd_expert_mtu <- round(sd(df_aoi_sum$Number_fixation_min_mtu[df_aoi_sum$Group == "Expert"], na.rm = TRUE), 2)

# 4. Perform t-test to get the p-value
t_test_mtu <- t.test(
  Number_fixation_min_mtu ~ Group,
  data = df_aoi_sum,
  var.equal = TRUE
)
p_value_mtu <- round(t_test_mtu$p.value, 2)

# 5. Calculate Cohen's d for effect size using formula syntax
library(effsize)
cohen_d_mtu <- round(cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)$estimate, 2)

# 6. Plotting the Number of Fixations per Minute (Micro-Teaching Unit)
y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5

plot_number_group <- df_aoi_sum %>%
  ggplot(mapping = aes(x = Group, y = Number_fixation_min_mtu)) +
  geom_boxplot(mapping = aes(fill = Group), outlier.shape = NA, width = 0.5) +
  geom_jitter(
    width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5
  ) +
  ylim(0, y_max_mtu) +
  labs(x = "", y = "Number of Fixations per Minute") +
  scale_fill_brewer(palette = "RdBu") +
  ggtitle("Number of Fixations per Minute\n(Micro-Teaching Unit)") +
  theme_cowplot() +
  theme(legend.position = "none") +
  # Annotations for mean (M) and SD using atop() to place SD below M
  annotate("text", x = 1, y = y_max_mtu * 0.85,
           label = paste0("atop(italic(M) == ", mean_novice_mtu, ", italic(SD) == ", sd_novice_mtu, ")"),
           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
  annotate("text", x = 2, y = y_max_mtu * 0.85,
           label = paste0("atop(italic(M) == ", mean_expert_mtu, ", italic(SD) == ", sd_expert_mtu, ")"),
           hjust = 0.5, size = 3.5, vjust = -0.5, parse = TRUE) +
  # Add p-value and Cohen's d annotations above the boxplots
  annotate("text", x = 1.5, y = y_max_mtu * 0.95,
           label = paste0("p = ", p_value_mtu, "\nd = ", cohen_d_mtu),
           hjust = 0.5, size = 4, fontface = "italic")

plot_number_group

ggsave(filename = "plots/plot_number_group.svg",
       width = 20,
       height = 12,
       units = "cm")

# 7. Format the t-Test and Cohen's d results for APA Table
t_test_result <- data.frame(
  "Group Comparison" = "Experts vs. Novices",
  "t-value" = round(t_test_mtu$statistic, 2),
  "df" = t_test_mtu$parameter,
  "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
  "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
  "Cohen's d" = cohen_d_mtu,
  "95% CI (d)" = paste0("[", round(t_test_mtu$conf.int[1], 2), ", ", round(t_test_mtu$conf.int[2], 2), "]")
)

# Display t-Test and Effect Size results in APA style
knitr::kable(t_test_result, caption = "t-Test and Effect Size for Number of Fixations per Minute (Micro-Teaching Unit)") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

>>>>

library(needs)
needs(
  tidyverse,     # A collection of packages (e.g., ggplot2, dplyr, tidyr) for data manipulation, visualization, and general workflows.
  lubridate,     # For working with dates and times (e.g., parsing, manipulation, arithmetic).
  viridis,       # Provides colorblind-friendly color palettes for plots and visualizations.
  grid,          # A base R package for low-level grid graphics, useful for customizing complex plots.
  gridExtra,     # Extends grid by allowing multiple grid-based plots to be arranged into a single layout.
  cowplot,       # Simplifies creating publication-quality multi-panel plots, often combined with ggplot2.
  readxl,        # For reading Excel files (.xls, .xlsx) into R without requiring external dependencies.
  ARTofR,        # For applying aligned rank transform (ART) to factorial data for nonparametric analysis.
  moments,       # Provides functions to compute statistical moments (e.g., skewness, kurtosis).
  ltm,           # Used for latent trait models, including item response theory (IRT) analysis.
  sjPlot,        # A package to create publication-ready tables and visualizations for statistical models.
  kableExtra,    # Enhances the `knitr::kable()` function for producing polished and customizable tables in R Markdown.
  xtable,        # Converts R objects to LaTeX/HTML tables, especially useful for integration with Sweave/knitr.
  DescTools,     # A toolbox of descriptive statistics, effect size calculations, and data manipulation utilities.
  formattable,   # Allows creation of "formattable" data frames with customized formatting for reporting.
  psych,         # Provides tools for psychological research, including reliability analysis and descriptive statistics.
  apaTables,     # Simplifies the creation of APA-style tables for inclusion in papers or reports.
  rstatix,       # User-friendly pipe-compatible functions for common statistical tests and effect sizes.
  effsize,       # Computes effect sizes (e.g., Cohen's d) for t-tests and other statistical comparisons.
  knitr,         # Enables dynamic reporting by weaving R code and outputs into documents (e.g., R Markdown).
  papaja,        # Helps produce APA-style manuscripts directly from R Markdown.
  afex,          # Performs ANOVAs, including mixed-designs and generalized linear models, with a focus on user-friendliness.
  emmeans,       # Computes estimated marginal means (or least-squares means) for post-hoc comparisons in models.
  corrplot,      # Visualize correlation matrices in a visually appealing way.
  flextable,     # Allows for creating customizable and professional tables
  officer        # Enables integration of tables and content into Microsoft Office documents like Word and PowerPoint
)

@@

# Gaze Allocation Across Areas of Interest 
```{r nof__dur_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#### Percentage of fixations on each AOI, relative to the total number of fixations during the entire "Lesson" 
# Step 1: Define AOI categories
aoi_columns <- list(
  "AOI_Students" = c(
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ),
  "AOI_Disruptive_Person" = c("Number_of_fixations.Disruptive_Person"),
  "AOI_Teacher_Material" = c(
    "Number_of_fixations.Board_Screen",
    "Number_of_fixations.Material_Teacher"
  ),
  "AOI_Student_Desk" = c(
    "Number_of_fixations.Nametag_Anna",
    "Number_of_fixations.Nametag_Bianca",
    "Number_of_fixations.Nametag_Carl(a)",
    "Number_of_fixations.Material_Students"
  ),
  "AOI_Classroom_Others" = c("Number_of_fixations.Classroom_Others")
)

@@

# Step 6: Restructure data for grouping and calculate 95% CI
grouped_aoi_percentages_ci <- aoi_percentages %>%
  pivot_longer(
    cols = starts_with("AOI"),
    names_to = "AOI",
    values_to = "Percentage"
  ) %>%
  mutate(AOI = recode(
    AOI,
    "AOI_Students_pct" = "Students",
    "AOI_Disruptive_Person_pct" = "Disruptive Person",
    "AOI_Teacher_Material_pct" = "Teacher Material",
    "AOI_Student_Desk_pct" = "Student Desk",
    "AOI_Classroom_Others_pct" = "Classroom/Others"
  )) %>%
  group_by(Group, AOI) %>%
  summarise(
    Mean_Percentage = mean(Percentage, na.rm = TRUE),
    CI_Lower = Mean_Percentage - qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
    CI_Upper = Mean_Percentage + qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

# Step 7: Plot with 95% confidence intervals
percentage_number_fixation <- ggplot(
  grouped_aoi_percentages_ci %>% 
    mutate(Group = recode(Group, 
                          "Expert" = "Experienced", 
                          "Novice" = "Inexperienced")),  # Rename groups
  aes(
    x = reorder(AOI, -Mean_Percentage),
    y = Mean_Percentage,
    fill = Group
  )
) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(
    aes(ymin = CI_Lower, ymax = CI_Upper),
    position = position_dodge(width = 0.8),
    width = 0.2
  ) +
  geom_text(
    aes(label = paste0(round(Mean_Percentage, 2), "%")),
    position = position_dodge(width = 0.8),
    vjust = -2.5,  # Adjusted to place the labels above the bars
    size = 3
  ) +
  labs(title = "Average Fixation Number Percentage by AOI and Group", 
       x = "AOI", 
       y = "Fixation Percentage (%)") +
  scale_fill_brewer(palette = "RdBu") +
  theme_cowplot() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  guides(fill = guide_legend(title = "Group"))

percentage_number_fixation

# Save the updated plot
ggsave(filename = "plots/percentage_number_fixation_with_ci.svg",
       width = 20,
       height = 12,
       units = "cm")

@@

# Initialize an empty data frame to store the results
results_number <- data.frame()

@@

      # Format the results_number for the current AOI and add to the results_number data frame
      results_number <- rbind(
        results_number,
        data.frame(
          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
          "Group Comparison" = "Experts vs. Novices",
          "t-value" = round(t_test_result$statistic, 2),
          "df" = t_test_result$parameter,
          "p-value" = format.pval(t_test_result$p.value, digits = 2, eps = .05),
          "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
          "Cohen's d" = round(cohen_d_value, 2),
          "95% CI (d)" = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
        )
      )

    } else {
      # If one group has no data, append N/A values for this AOI
      results_number <- rbind(
        results_number,
        data.frame(
          "AOI" = gsub("_pct", "", column_name),  # Remove "_pct" suffix for readability
          "Group Comparison" = "Experienced vs. Inexperienced",
          "t-value" = NA,
          "df" = NA,
          "p-value" = NA,
          "Mean Difference" = NA,
          "Cohen's d" = NA,
          "95% CI (d)" = NA
        )
      )
    }
  }
}

# Clean up AOI names for readability in the final table
aoi_name_mapping <- c(
  "AOI_Students" = "Students",
  "AOI_Disruptive_Person" = "Disruptive Person",
  "AOI_Teacher_Material" = "Teacher Material",
  "AOI_Student_Desk" = "Student Desk",
  "AOI_Classroom_Others" = "Classroom/Others"
)
results_number$AOI <- aoi_name_mapping[results_number$AOI]

# Display the combined results_number table in APA style without row names
knitr::kable(results_number, caption = "t-Test and Effect Size for Fixation Percentage across AOIs (Experts vs. Novices)", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

#### Percentage of fixation durations on each AOI, relative to the total duration of fixations during the entire "Lesson" 
# Step 1: Define AOI categories with correct column names for fixation duration
aoi_columns <- list(
  "AOI_Students" = c(
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)"
  ),
  "AOI_Disruptive_Person" = c("Total_duration_of_fixations.Disruptive_Person"),
  "AOI_Teacher_Material" = c(
    "Total_duration_of_fixations.Board_Screen",
    "Total_duration_of_fixations.Material_Teacher"
  ),
  "AOI_Student_Desk" = c(
    "Total_duration_of_fixations.Nametag_Anna",
    "Total_duration_of_fixations.Nametag_Bianca",
    "Total_duration_of_fixations.Nametag_Carl(a)",
    "Total_duration_of_fixations.Material_Students"
  ),
  "AOI_Classroom_Others" = c("Total_duration_of_fixations.Classroom_Others")
)

# Step 6: Restructure data for grouping and calculate 95% CI for fixation durations
grouped_aoi_durations_ci <- aoi_durations_percentages %>%
  pivot_longer(
    cols = starts_with("AOI"),
    names_to = "AOI",
    values_to = "Duration_Percentage"
  ) %>%
  mutate(AOI = recode(
    AOI,
    "AOI_Students_pct" = "Students",
    "AOI_Disruptive_Person_pct" = "Disruptive Person",
    "AOI_Teacher_Material_pct" = "Teacher Material",
    "AOI_Student_Desk_pct" = "Student Desk",
    "AOI_Classroom_Others_pct" = "Classroom/Others"
  )) %>%
  group_by(Group, AOI) %>%
  summarise(
    Mean_Duration_Percentage = mean(Duration_Percentage, na.rm = TRUE),
    CI_Lower = Mean_Duration_Percentage - qt(0.975, df = n() - 1) * sd(Duration_Percentage, na.rm = TRUE) / sqrt(n()),
    CI_Upper = Mean_Duration_Percentage + qt(0.975, df = n() - 1) * sd(Duration_Percentage, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

# Step 7: Plot with 95% confidence intervals
percentage_duration_fixation <- ggplot(
  grouped_aoi_durations_ci %>%
    mutate(Group = recode(Group, "Expert" = "Experienced", "Novice" = "Inexperienced")), # Rename groups
  aes(
    x = reorder(AOI, -Mean_Duration_Percentage),
    y = Mean_Duration_Percentage,
    fill = Group
  )
) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(
    aes(ymin = CI_Lower, ymax = CI_Upper),
    position = position_dodge(width = 0.8),
    width = 0.2
  ) +
  geom_text(
    aes(label = paste0(round(Mean_Duration_Percentage, 2), "%")),
    position = position_dodge(width = 0.8),
    vjust = -2.5,  # Adjusted to place the labels above the bars
    size = 3
  ) +
  ylim(0, 60) + 
  labs(
    title = "Average Fixation Duration Percentage by AOI and Group",
    x = "AOI",
    y = "Fixation Duration Percentage (%)"
  ) +
  scale_fill_brewer(palette = "RdBu") +
  theme_cowplot() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  guides(fill = guide_legend(title = "Group"))
percentage_duration_fixation

ggsave(
  filename = "plots/percentage_duration_fixation_with_ci.svg",
  width = 20,
  height = 12,
  units = "cm"
)

# Step 7: Perform a t-test between Experts and Novices on the duration percentages and calculate Cohen's d
aoi_list <- c("AOI_Students_pct", "AOI_Disruptive_Person_pct", "AOI_Teacher_Material_pct", "AOI_Student_Desk_pct", "AOI_Classroom_Others_pct")
results_duration <- data.frame()

      results_duration <- rbind(
        results_duration,
        data.frame(
          "AOI" = gsub("_pct", "", column_name),
          "Group Comparison" = "Experts vs. Novices",
          "t-value" = round(t_test_result$statistic, 2),
          "df" = t_test_result$parameter,
          "p-value" = format.pval(t_test_result$p.value, digits = 2, eps = .05),
          "Mean Difference" = round(t_test_result$estimate[1] - t_test_result$estimate[2], 2),
          "Cohen's d" = round(cohen_d_value, 2),
          "95% CI (d)" = paste0("[", round(t_test_result$conf.int[1], 2), ", ", round(t_test_result$conf.int[2], 2), "]")
        )
      )
    } else {
      results_duration <- rbind(
        results_duration,
        data.frame(
          "AOI" = gsub("_pct", "", column_name),
          "Group Comparison" = "Experienced vs. Inexperienced",
          "t-value" = NA,
          "df" = NA,
          "p-value" = NA,
          "Mean Difference" = NA,
          "Cohen's d" = NA,
          "95% CI (d)" = NA
        )
      )
    }
  }
}

# Map AOI names to clean versions for readability in the final results_duration table
results_duration$AOI <- recode(results_duration$AOI,
                      "AOI_Students" = "Students",
                      "AOI_Disruptive_Person" = "Disruptive Person",
                      "AOI_Teacher_Material" = "Teacher Material",
                      "AOI_Student_Desk" = "Student Desk",
                      "AOI_Classroom_Others" = "Classroom/Others")

# Display the t-Test and Effect Size table in APA style
knitr::kable(results_duration, 
             caption = "t-Test and Effect Size for Fixation Duration Percentage across AOIs (Experts vs. Novices)", 
             row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

@@

#### Number of fixations per minute and fixation duration in ms (micro-teaching unit)
```{r nof_dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
##################### NUMBER OF FIXATIONS PER MINUTE ########################

##################### Data Preparation ########################
df_aoi_sum <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Group,
    Participant,
    Duration_of_interval,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    -contains("Disruptive_Person")
  ) %>%
  rowwise() %>%
  transmute(
    Group = factor(Group, levels = c("Expert", "Novice"), labels = c("Experienced", "Inexperienced")),
    Participant,
    Duration_of_interval_min = Duration_of_interval / 60000,
    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Number_fixation_min_mtu = Sum_number_fixation / Duration_of_interval_min,
    Avg_fixation_duration = Sum_duration_fixation / Sum_number_fixation
  ) %>%
  drop_na()

##################### Number of Fixations per Minute ########################

# Descriptive Statistics for Number of Fixations per Minute
nof_stats <- df_aoi_sum %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    M = round(mean(Number_fixation_min_mtu, na.rm = TRUE), 2),
    SD = round(sd(Number_fixation_min_mtu, na.rm = TRUE), 2),
    Min = round(min(Number_fixation_min_mtu, na.rm = TRUE), 2),
    Max = round(max(Number_fixation_min_mtu, na.rm = TRUE), 2)
  )

# Display Table
knitr::kable(nof_stats, caption = "N, M, SD, Min & Max for Number of Fixations per Minute") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# t-Test and Cohen's d
t_test_mtu <- t.test(Number_fixation_min_mtu ~ Group, data = df_aoi_sum, var.equal = TRUE)
cohen_d_mtu <- cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)

# APA Table
t_test_result_mtu <- data.frame(
  "Group Comparison" = "Experienced vs. Inexperienced",
  "t-value" = round(t_test_mtu$statistic, 2),
  "df" = t_test_mtu$parameter,
  "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
  "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
  "Cohen's d" = round(cohen_d_mtu$estimate, 2),
  "95% CI (d)" = paste0("[", round(cohen_d_mtu$conf.int[1], 2), ", ", round(cohen_d_mtu$conf.int[2], 2), "]")
)

knitr::kable(t_test_result_mtu, caption = "t-Test and Effect Size for Number of Fixations per Minute") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# Ensure cohen_d_mtu is numeric
cohen_d_mtu <- round(as.numeric(cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)$estimate), 2)

# Plot: Number of Fixations per Minute
y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5

plot_number_fixation_group <- df_aoi_sum %>%
  ggplot(aes(x = Group, y = Number_fixation_min_mtu, fill = Group)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
  scale_fill_brewer(palette = "RdBu") +
  ylim(0, y_max_mtu) +
  labs(title = "Number of Fixations per Minute\n(Micro-Teaching Unit)", x = "", y = "Fixations per Minute") +
  theme_cowplot() +
  theme(legend.position = "none") +
  annotate("text", x = 1, y = 3,
           label = paste0("italic(M) == ", round(nof_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[1], 2)),
           hjust = 0.5, size = 4, parse = TRUE) +
  annotate("text", x = 2, y = 3,
           label = paste0("italic(M) == ", round(nof_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[2], 2)),
           hjust = 0.5, size = 4, parse = TRUE) +
  annotate("text", x = 1.5, y = y_max_mtu * 0.95,
           label = paste0("italic(p) == ", round(t_test_mtu$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_mtu),
           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)

plot_number_fixation_group

ggsave(filename = "plots/plot_number_fixation_group.svg",
       width = 20,
       height = 12,
       units = "cm")

##################### Average Fixation Duration ########################

# Descriptive Statistics for Average Fixation Duration
fixation_stats <- df_aoi_sum %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    M = round(mean(Avg_fixation_duration, na.rm = TRUE), 2),
    SD = round(sd(Avg_fixation_duration, na.rm = TRUE), 2),
    Min = round(min(Avg_fixation_duration, na.rm = TRUE), 2),
    Max = round(max(Avg_fixation_duration, na.rm = TRUE), 2)
  )

# Display Table
knitr::kable(fixation_stats, caption = "N, M, SD, Min & Max for Average Fixation Duration") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# t-Test and Cohen's d
t_test_fixation <- t.test(Avg_fixation_duration ~ Group, data = df_aoi_sum, var.equal = TRUE)
cohen_d_fixation <- cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)

# APA Table
t_test_result_fixation <- data.frame(
  "Group Comparison" = "Experienced vs. Inexperienced",
  "t-value" = round(t_test_fixation$statistic, 2),
  "df" = t_test_fixation$parameter,
  "p-value" = format.pval(t_test_fixation$p.value, digits = 2, eps = .05),
  "Mean Difference" = round(t_test_fixation$estimate[1] - t_test_fixation$estimate[2], 2),
  "Cohen's d" = round(cohen_d_fixation$estimate, 2),
  "95% CI (d)" = paste0("[", round(cohen_d_fixation$conf.int[1], 2), ", ", round(cohen_d_fixation$conf.int[2], 2), "]")
)

knitr::kable(t_test_result_fixation, caption = "t-Test and Effect Size for Average Fixation Duration") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# Ensure cohen_d_fixation is numeric
cohen_d_fixation <- round(cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)$estimate, 2)

# Plot: Average Fixation Duration
plot_avg_fixation_group <- df_aoi_sum %>%
  ggplot(aes(x = Group, y = Avg_fixation_duration, fill = Group)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
  scale_fill_brewer(palette = "RdBu") +
  labs(title = "Average Fixation Duration\n(Micro-Teaching Unit)", x = "", y = "Fixation Duration (ms)") +
  theme_cowplot() +
  theme(legend.position = "none") +
  # Add M and SD values below the x-axis for each group
  annotate("text", x = 1, y = -50,  # Adjust y-coordinate to place below the x-axis
           label = paste0("italic(M) == ", round(fixation_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[1], 2)),
           hjust = 0.5, size = 4, parse = TRUE) +
  annotate("text", x = 2, y = -50,  # Adjust y-coordinate to place below the x-axis
           label = paste0("italic(M) == ", round(fixation_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[2], 2)),
           hjust = 0.5, size = 4, parse = TRUE) +
  # Add p-value and d-value above the plot
  annotate("text", x = 1.5, y = max(df_aoi_sum$Avg_fixation_duration) * 1.1,
           label = paste0("italic(p) == ", round(t_test_fixation$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_fixation),
           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)

ggsave(filename = "plots/plot_avg_fixation_group.svg",
       width = 20,
       height = 12,
       units = "cm")

# Load the patchwork library
install.packages("patchwork")
library(patchwork)

# Combine the two plots side by side
combined_plot <- plot_number_fixation_group + plot_avg_fixation_group +
  plot_layout(ncol = 2, guides = "collect") &
  theme(legend.position = "none")

# Display the combined plot
combined_plot

# Save the combined plot
ggsave(
  filename = "plots/combined_results_plot.svg",
  plot = combined_plot,
  width = 25,
  height = 12,
  units = "cm"
)

@@

### Duration of disruption
